Gradual Soundness: Lessons from Static Python

### 2022-01-12 pj-7.1/paper.tex
abstract cleanup

@@

  \paragraph{Approach}
  % What was done that unveiled new knowledge?
  In collaboration with the \SP{} team, we have evaluated the language
  as it exists today and developed a model to capture the essence of its
  approach to gradual types.
  We drew upon personal communications, bug reports, and the \SP{}
  regression test suite.

  \paragraph{Knowledge}
  % What new facts were uncovered? If the
  % research was not results oriented, what new
  % capabilities are enabled by the work?
  Our main finding is that the \emph{gradual soundness}\/ that
  arises from a mix of concrete and transient types is an effective
  way to lower the maintenance cost of the concrete approach.
  On a more technical level, this paper contributes two artifacts:
  a model of \SP{} that passes all relevant tests from the \SP{} codebase
  and a performance evaluation of \SP{}.

>>>>

  \vglue10pt

@@

  \vglue10pt

  \paragraph{Approach}
  % What was done that unveiled new knowledge?
  We evaluate the language in its current state
  to develope a model that capture the essence of its
  approach to gradual types.
  We draw upon personal communication, bug reports, and the \SP{}
  regression test suite to develop this model.

  \vglue10pt

  \paragraph{Knowledge}
  % What new facts were uncovered? If the
  % research was not results oriented, what new
  % capabilities are enabled by the work?
  Our main finding is that the \emph{gradual soundness}\/ that
  arises from a mix of concrete and transient types is an effective
  way to lower the maintenance cost of the concrete approach.
  On a more technical level, this paper contributes two artifacts:
  a model of \SP{} that passes all relevant tests from the \SP{} codebase,
  and a performance evaluation of \SP{}. The process of formalization
  has also found several errors in the implementation, inlcuding fatal errors.

  \vglue10pt
